---
title: "Chocolate Souffle"
date: 11-08-2025 
date-modified: last-modified
format: 
  html:
    date-format: long
---

```{r}
#| label: load-packages
#| include: false

library(tibble)
library(gt)
source("utility_functions.R")
```


### **Chocolate Souffles (amount: two 8oz ramekins)**
```{r}
#| label: recipe
#| echo: false
ingredients <- list(
  "1. large eggs (50g each without shell)" = "2",
  "2. chocolate (60 to 65 percent cacao)" = "75 g",
  "3. unsalted butter" = "38 g",
  "4. sugar for egg white" = "16 g",
  "5. sea salt" = "pinch",
  "6. powder sugar" = "1 Tbsp"
)

make_ingredient_tab(ingredients)
```


## Step by Step

1. Grease ramekins with butter and coat with sugar.
2. Melt chocolate and butter over simmering water. 
3. Let the chocolate cool slight to warm and add egg yolks and salt.
4. Whisk the egg white with a hand mixer and add sugar 1/3 at a time, until soft peaks. 
5. Whip the mixture in step 3 with a hand mixer.
6. Fold in the meringue 1/3 at a time with a spatula.
7. Divide the batter among the ramekins. 
8. Bake at 400F for about 15mins
9. Dust with powdered sugar immediately after taking out.

## SZzZz's Notes:
Notes for coating the ramekins [Sara Z’s Notes/Tips in the vanilla souffle recipe](https://sarazong.github.io/Baking-Project/recipes/vanilla_souffle_lemon_curd.html)

## Recipe Credits:
- Original Recipe from [New York Times](https://cooking.nytimes.com/recipes/1018499-bittersweet-chocolate-souffle){target="_blank"}

